Prospective simulation

### 2021-03-10 scripts/r/simulations/simulations.Rmd
:memo: - edit simulation.Rmd with explanations

```{r prior-predictive}
meta_bm_ppred <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  sample_prior = "only",
  chain = 4,
  seed = my_seed,
  file = "./models/sim/meta_bm_ppred"
)

ppred_samples <- posterior_samples(meta_bm_ppred) %>%
  rename(intercept = b_Intercept, `group-level SD` = sd_team__Intercept)
```

```{r ppred-posts}
ppred_samples %>%
  pivot_longer(intercept:`group-level SD`, names_to = "term") %>%
  mutate(term = factor(term, levels = c("intercept", "group-level SD"))) %>%
  ggplot(aes(value)) +
  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 0.4) +
  facet_wrap(~ term, scales = "free")
```

@@

>>>>

Prior predictive checks are run to assess the goodness of the prior specification before model fitting.

```{r prior-predictive}
# run checks
meta_bm_ppred <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  sample_prior = "only",
  chain = 4,
  seed = my_seed,
  file = "./models/sim/meta_bm_ppred"
)

# get samples
ppred_samples <- posterior_samples(meta_bm_ppred) %>%
  rename(intercept = b_Intercept, `group-level SD` = sd_team__Intercept)
```

Let's plot the prior probability distributions of the intercept and the standard deviation.

```{r ppred-posts, message=FALSE, warning=FALSE}
ppred_long <- ppred_samples %>%
  pivot_longer(intercept:`group-level SD`, names_to = "term") %>%
  mutate(term = factor(term, levels = c("intercept", "group-level SD")))

int <- ppred_long %>%
  filter(term == "intercept") %>%
  ggplot(aes(value)) +
  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 0.4) +
  labs(title = "Intercept")

sd <- ppred_long %>%
  filter(term == "group-level SD") %>%
  ggplot(aes(value)) +
  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 1) +
  xlim(0, 25) +
  labs(title = "Group-level SD")

int + sd
```

And the joint prior probability distribution.

@@

The following code fits the meta-analytical model to the simulated data.
